---
title: 'Remote sensing and image processing: how to load csv files'
output:
  html_document:
    df_print: paged
  pdf_document: default
---

## Load the data

1-The data is loaded using read.csv function:

```{r load csv files, echo=T}
folder = "/home/philipp/Documents/boku/remote_sensing_image_processing/lecture_5_classification/data"
csv_file="data_classification.csv"
root = file.path(folder,csv_file)
MyData <- read.csv(file=root, header=TRUE, sep=",")
```

# Data visualization

1-It is possible visualize the Table:

```{r see what are inside of MyData, echo=TRUE}
MyData[1:15,1:dim(MyData)[2]]
```
# A-Plot the histograms of the classes:

```{r Histogram of the classes, echo=T}
h<-hist(MyData[1:dim(MyData)[1],2],
     main="Histogram for classes", 
     xlab="Classes", 
     border="blue", 
     col="red",
     xlim=c(0,10),
     ylim=c(0,2300),
     breaks=20)
text(h$mids,h$counts,labels=h$counts, adj=c(0.5, -0.5))
```

# B-Plot the reflectance average per class:
B1.1- Find the reflectances for class 1:
```{r find the reflectances for class 1, echo=T}
# index positions of class 1 in csv file:
ind_cl_1 = which(MyData[1:dim(MyData)[1],2] == 1)
length(ind_cl_1)
```

B1.2- Calculate the average of reflectances for class 1:
```{r Calculate the average of reflectances for class 1, echo=T}
# Average of all pixel class 1 values per band:  
mean_cl = sapply(MyData[ind_cl_1,3:dim(MyData)[2]], mean, na.rm = TRUE)
mean_cl
``` 

B1.3- Plot the average of reflectances for class 1:
```{r Plot the average of reflectances for class 1, echo=T}
plot(mean_cl, ylim=c(300,4000),type="b" , lwd=3 , col=rgb(0.1,0.7,0.1,0.8),
     ylab="reflectance" , xlab="Bands" , bty="l" , pch=20 , cex=2, xaxt="n")
grid (NULL,NULL, lty = 6, col = "cornsilk2")
axis(1, at=seq(1,9,1),labels=c("B2", "B3", "B4","B5","B6","B7","B8A","B11","B12"), las=0)
legend(x=1, y=4000,legend="Class 1", pch=20, col=rgb(0.1,0.7,0.1,0.8),text.font=3, 
       lty=c(1,1,1,1,1,1,1), cex=0.7, horiz = F, xpd=TRUE)
 
```

B2.1- Find the reflectances for class 2:
```{r find the reflectances for class 2, echo=T}
# index positions of class 1 in csv file:
ind_cl_2 = which(MyData[1:dim(MyData)[1],2] %in% 7)
length(ind_cl_2)
```

B1.2- Calculate the average of reflectances for class 2:
```{r Calculate the average of reflectances for class 2, echo=T}
# Average of all pixel class 1 values per band:  
mean_cl = sapply(MyData[ind_cl_2,3:dim(MyData)[2]], mean, na.rm = TRUE)
mean_cl
``` 

B1.3- Plot the average of reflectances for class 2:
```{r Plot the average of reflectances for class 2, echo=T}
plot(mean_cl, ylim=c(300,4000),type="b" , lwd=3 , col=rgb(0.7,0.7,0.1,0.8),
     ylab="reflectance" , xlab="Bands" , bty="l" , pch=20 , cex=2, xaxt="n")
grid (NULL,NULL, lty = 6, col = "cornsilk2")
axis(1, at=seq(1,9,1),labels=c("B2", "B3", "B4","B5","B6","B7","B8A","B11","B12"), las=0)
legend(x=1, y=4000,legend="Class 2", pch=20, col=rgb(0.7,0.7,0.1,0.8),text.font=3, 
       lty=c(1,1,1,1,1,1,1), cex=0.7, horiz = F, xpd=TRUE)
```

# Exercise 1:
```{r Exercise 1, echo=T}
# Plot of average of reflectances for all the classes and upload it in Boku learn, Exercise 8.
for (i in 1:max(MyData$class_id)) {
  # filter class
  ind_cl = which(MyData[1:dim(MyData)[1],2] == i)
  # Average of all pixel class 1 values per band:  
  mean_cl = sapply(MyData[ind_cl,3:dim(MyData)[2]], mean, na.rm = TRUE)
  # create string for legend
  class_i <- paste("Class", i, sep =" ")
  # plot mean reflectance
  plot(mean_cl, ylim=c(300,7000),type="b" , lwd=3 , col=i,#rgb(0.7,0.7,0.1,0.8),
      ylab="reflectance" , xlab="Bands" , bty="l" , pch=20 , cex=2, xaxt="n")
  grid (NULL,NULL, lty = 6, col = "cornsilk2")
  axis(1, at=seq(1,9,1),labels=c("B2", "B3", "B4","B5","B6","B7","B8A","B11","B12"), las=0)
  legend(x=1, y=4000,legend=class_i, pch=20, col=i, text.font=3, 
         lty=c(1,1,1,1,1,1,1), cex=0.7, horiz = F, xpd=TRUE)
}
```