---
title: "Minimum distance classifier"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

## Load the data

1-The data is loaded using read.csv function:
```{r load csv files, echo=T}
root = '/home/philipp/Documents/boku/remote_sensing_image_processing/lecture_5_classification/data'
file = "data_classification.csv"
csv_file = file.path(root, file)
MyData <- read.csv(file=csv_file, header=TRUE, sep=",")
MyData[1:15,1:dim(MyData)[2]]
```
We can know how many samples there are in the table:
```{r}
sprintf('total set contains %s samples and %s features', dim(MyData)[1], dim(MyData)[2])
```

## 2. Split the data:
```{r Find the indeces of the samples to training and test:}
set.seed(3333)
ind = sample(dim(MyData)[1])
percen = 75
ind_tr = ind[1:(dim(MyData)[1]*percen/100)]
length(ind_tr)
ind_ts = ind[((dim(MyData)[1]*percen/100)+1):dim(MyData)[1]]
length(ind_ts)
```

We can know the number of samples in the training set:
```{r Select a percentage of the original data and generate balanced training subsets:}
X_tr = MyData[ind_tr,3:11]
Y_tr = MyData[ind_tr,2]
sprintf('training set contains %s samples and %s features', dim(X_tr)[1], dim(X_tr)[2])
```

We can know the number of samples in the test set:
```{r Select a percentage of the original data and generate balanced test subsets:}
X_ts = MyData[ind_ts,3:11]
Y_ts = MyData[ind_ts,2]
sprintf('Test subset contains %s samples and %s features', dim(X_ts)[1], dim(X_ts)[2])
```

## 3. Minimum distance classifier:

```{r n-dimansionality mean per class:}
mean_cl <- NULL
classes = unique(Y_tr)
for (cl in seq(1,length(classes),1)) {
        ind_cl = which(Y_tr %in% classes[cl])
        mean_cls = sapply(X_tr[ind_cl,1:dim(X_tr)[2]], mean, na.rm = TRUE)
        mean_cl <-rbind(mean_cl,mean_cls) 
}
mean_cl

```
Minimum distance regarding to the mean: minimum distance from the training mean: The classifier will assign the class of the group which its mean is closed to the test sample:
```{r B-minimum distance classifier}
  #Calculating distances
prediction <- NULL
X_train <- as.matrix(X_tr)
X_test <- as.matrix(X_ts)
m <- dim(mean_cl)[1]
n <- dim(X_test)[1]

for (j in 1:n)
{
    dist_cl <- sqrt(rowSums((as.matrix(mean_cl) - t(replicate(m, X_test[j,])))^2, 
                            na.rm = TRUE))
    Y_pred = classes[which.min(dist_cl)]
    prediction<-cbind(prediction,Y_pred)
}
prediction <- (t(prediction))

#Predicting
predictions <- data.frame(predicted = prediction, ground_true = Y_ts)

```

# Assessment:
```{r A-Confusion matrix:}
#function
accuracy <- function (pred,actual)
{
    conf_matrix <- table(predictions = pred, actual = actual)
    sum <- 0
    for (j in 1:dim(conf_matrix)[2])
        for (i in 1:dim(conf_matrix)[1])
            if (j == i)
                sum<-sum+conf_matrix[i,j]
    return(list(conf_matrix,sum/length(pred)*100))
}

accuracy(predictions$predicted,predictions$ground_true)
```

# Exercise 4:
```{r Exercise 4, echo=T}
# Use the minimum distance classifier with a training set that have equal number of samples per class and upload it in Boku learn, Exercise 9.
```
